Curriculum and Imitation Learning for Biped Locomotion on Rough Terrain

### 2019-02-02 paper/rss/main.tex
edits to introduction
Fix some TODOs in the paper

In subsequent subsections, it will be helpful to have in mind a concrete example of this kind of TG.
For biped locomotion, our TG is a modification of the walking gait from SIMBICON \citep{yin2007simbicon}.
SIMBICON uses a finite state machine (FSM) with two states: an UP state that ends after 0.3 seconds, and a DOWN state that ends on swing foot contact.
During each state, proportional derivative (PD) controllers attempt to reach the corresponding set of target joint angles.
Balance feedback is achieved by adjusting the target swing hip angles based on the distance and velocity of the agent's CoM relative to its stance foot contact location.
After hand-tuning the balance feedback gains and the joint angles for each state, this simple control scheme can walk forward and maintain its balance.
We make several novel modifications to SIMBICON in order to control its footstep placement more precisely:\footnote{
For more details, see Appendix \ref{app:simbicon}.}
\begin{enumerate}
  \item Insert a new TOE-OFF state at the beginning of each step.
    This state transitions to the UP state after 0.2s.
    It is identical to the UP state except that the target swing ankle angle can be modified by the parameter \texttt{toe\_off\_ankle}.
    This allows the HLP to use the swing ankle to influence the robot's initial acceleration while still returing to a more neutral angle before heel-strike.

@@

Even without a curriculum, the algorithm is able to find a policy that \emph{usually} achieves high reward.
However, CIM reaches the same median performance twice as quickly.
The story is similar for fifth-percentile performance.
\nhatch{TODO finish this once rerunning experiments finish}

@@

In particular, CIM is an intriguing direction for biped locomotion research.
To the best of our knowledge, our experiments are the first to achieve such precise foot placement
using a fast, dynamic gait that requires no optimization during policy execution.
However, one significant limitation of our work so far is that all experiments were performed in simulation.
In future work, we plan to investigate how to transfer policies trained with CIM to real-world bipedal robots.

\nhatch{future work: adaptive curriculum (adjusts to learner's current ability)}

>>>>

In subsequent subsections, it will be helpful to have in mind a concrete example of this kind of TG.
For biped locomotion, our TG is a modification of the walking gait from SIMBICON \citep{yin2007simbicon}.
SIMBICON uses a finite state machine (FSM) with two states: an UP state that ends after 0.3 seconds, and a DOWN state that ends on swing foot contact.
During each state, proportional derivative (PD) controllers attempt to reach the corresponding set of target joint angles.
Balance feedback is achieved by adjusting the target swing hip angles based on the distance and velocity of the agent's CoM relative to its stance foot contact location.
After hand-tuning the balance feedback gains and the joint angles for each state, this simple control scheme can walk forward and maintain its balance.
We make several novel modifications to SIMBICON in order to control its footstep placement more precisely:\footnote{
For more details, see Appendix \ref{app:simbicon} in the supplemental material.}
\begin{enumerate}
  \item Insert a new TOE-OFF state at the beginning of each step.
    This state transitions to the UP state after 0.2s.
    It is identical to the UP state except that the target swing ankle angle can be modified by the parameter \texttt{toe\_off\_ankle}.
    This allows the HLP to use the swing ankle to influence the robot's initial acceleration while still returing to a more neutral angle before heel-strike.

@@

Even without a curriculum, the algorithm is able to find a policy whose median performance completes all sixteen steps of an episode.
However, CIM reaches that same median performance three times as quickly.
Similarly, CIM's 10th-percentile performance is almost perfect with less than 6000 training footsteps, while without a curriculum it takes twice as long to reach that level.

@@

In particular, CIM is an intriguing direction for biped locomotion research.
To the best of our knowledge, our experiments are the first to achieve such precise foot placement
using a fast, dynamic gait that requires no optimization during policy execution.
However, one significant limitation of our work so far is that all experiments were performed in simulation.
In future work, we plan to investigate how to transfer policies trained with CIM to real-world bipedal robots.
We also plan to investigate whether it helps to have an \emph{adaptive} curriculum that adjusts to the learner's current ability.
